Measuring contrast processing in the visual system using SSVEP

### 2024-04-08 review.qmd
Added more figure cation, grids

```{python}
#| label: fig-plotclinical
#| fig-cap: "Example contrast response functions for different clinical conditions. Panel (a) shows modelled contrast response functions for epilepsy patients (blue) and control participants (black), based on the data of Tsai et al. (2011). Panel (b) shows functions for the amblyopic (red) and fellow (black) eyes of adults with amblyopia, based on the data of Baker et al. (2015). Panel (c) shows functions for children with (green) and without (black) a diagnosis of autism, based on the data of Vilidaite et al. (2018). Panel (d)"
#| fig-cap-location: bottom

@@

plt.figure(figsize=(12, 10))
plt.subplot(2, 2, 1)
plt.plot(finecontrastsdB, respEPIpatients, lw=4, color='blue', label='Epilepsy patients')
plt.plot(finecontrastsdB, respEPIcontrols, lw=4, color='black', linestyle='--', label='Control participants')
plt.xticks(ticklocsx, ticklabelsx)
plt.yticks(np.arange(0, 7, 2))
plt.xlabel('Target contrast (%)')
plt.ylabel('SSVEP response')
plt.title('(a) Epilepsy')
plt.legend()

@@

plt.subplot(2, 2, 2)
plt.plot(finecontrastsdB, respambly, lw=4, color='red', label='Amblyopic eye')
plt.plot(finecontrastsdB, respfellow, lw=4, color='black', linestyle='--', label='Fellow eye')
plt.xticks(ticklocsx, ticklabelsx)
plt.yticks(np.arange(0, 2.5, 0.5))
plt.xlabel('Target contrast (%)')
plt.ylabel('SSVEP response')
plt.title('(b) Amblyopia')
plt.legend()

@@

plt.subplot(2, 2, 3)  # Assuming this is the third plot for Autism
plt.plot(finecontrastsdB, respASD, lw=4, color='darkgreen', label='ASD children')
plt.plot(finecontrastsdB, respCON, lw=4, color='black', linestyle='--', label='Control children')
plt.xticks(ticklocsx, ticklabelsx)
plt.yticks(np.arange(0, 1.6, 0.5))
plt.xlabel('Target contrast (%)')
plt.ylabel('SSVEP response')
plt.title('(c) Autism')
plt.legend()

@@

plt.subplot(2, 2, 4)  # Fourth plot for Parkinson's
plt.plot(finecontrastsdB, respParkPatients, lw=4, color='red', label='hLRRK2 transgenic flies')
plt.plot(finecontrastsdB, respParkControls, lw=4, color='black', linestyle='--', label='TH+ (control) flies')
plt.xticks(ticklocsx, ticklabelsx)
plt.yticks(np.arange(0, 7, 2))
plt.xlabel('Target contrast (%)')
plt.ylabel('SSVEP response')
plt.title("(d) Parkinson's")
plt.legend()
# To save the figure
# plt.savefig('Figures/clinicalplot.pdf')
plt.show()

>>>>

```{python}
#| label: fig-plotclinical
#| fig-cap: "Example contrast response functions for different clinical conditions. Panel (a) shows modelled contrast response functions for epilepsy patients (blue) and control participants (black), based on the data of Tsai et al. (2011). Panel (b) shows functions for the amblyopic (red) and fellow (black) eyes of adults with amblyopia, based on the data of Baker et al. (2015). Panel (c) shows functions for children with (green) and without (black) a diagnosis of autism, based on the data of Vilidaite et al. (2018). Panel (d) shows data from *Drosophila melanogaster* (fruit flies) in Afsari et al 2014. One day-old flies expressing a human gene linked to Parkinson's (hLRRK-G2019S) show increased SSVEP response amplitude and sensitivity compared to control animals"
#| fig-cap-location: bottom

@@

plt.figure(figsize=(12, 10))
plt.subplot(2, 2, 1)
plt.plot(finecontrastsdB, respEPIpatients, lw=4, color='blue', label='Epilepsy patients')
plt.plot(finecontrastsdB, respEPIcontrols, lw=4, color='black', linestyle='--', label='Control participants')
plt.xticks(ticklocsx, ticklabelsx)
plt.yticks(np.arange(0, 7, 2))
plt.xlabel('Target contrast (%)')
plt.ylabel('SSVEP response')
plt.title('(a) Epilepsy')
plt.legend()
plt.grid()

@@

plt.subplot(2, 2, 2)
plt.plot(finecontrastsdB, respambly, lw=4, color='red', label='Amblyopic eye')
plt.plot(finecontrastsdB, respfellow, lw=4, color='black', linestyle='--', label='Fellow eye')
plt.xticks(ticklocsx, ticklabelsx)
plt.yticks(np.arange(0, 2.5, 0.5))
plt.xlabel('Target contrast (%)')
plt.ylabel('SSVEP response')
plt.title('(b) Amblyopia')
plt.legend()
plt.grid()

@@

plt.subplot(2, 2, 3)  # Assuming this is the third plot for Autism
plt.plot(finecontrastsdB, respASD, lw=4, color='darkgreen', label='ASD children')
plt.plot(finecontrastsdB, respCON, lw=4, color='black', linestyle='--', label='Control children')
plt.xticks(ticklocsx, ticklabelsx)
plt.yticks(np.arange(0, 1.6, 0.5))
plt.xlabel('Target contrast (%)')
plt.ylabel('SSVEP response')
plt.title('(c) Autism')
plt.legend()
plt.grid()

@@

plt.subplot(2, 2, 4)  # Fourth plot for Parkinson's
plt.plot(finecontrastsdB, respParkPatients, lw=4, color='red', label='hLRRK2 transgenic flies')
plt.plot(finecontrastsdB, respParkControls, lw=4, color='black', linestyle='--', label='TH+ (control) flies')
plt.xticks(ticklocsx, ticklabelsx)
plt.yticks(np.arange(0, 7, 2))
plt.xlabel('Target contrast (%)')
plt.ylabel('SSVEP response')
plt.title("(d) Parkinson's")
plt.legend()
plt.grid()

# To save the figure
# plt.savefig('Figures/clinicalplot.pdf')
plt.show()
